\LARGE \bf Mean Estimation from One-Bit Measurements

### 2021-10-01 response.tex

\begin{review}
(2) I think there are problems with the example in Appendix VII that demonstrates fast convergence in the case of uniform distribution. The initial estimate $\theta^{init}$ is set to be the maximal threshold for which $B_i$ = 0 for all observations corresponding to that threshold. But the way $B_i$ is defined, wouldn't this maximal threshold always be the very last threshold in the interval $[-n \epsilon, n \epsilon]$? If, instead, we interchange the roles of $0$ and $1$ in the defining $B_i$, then we might be on to something. But then, what confuses me is the statement: ``we always have $\theta^{init} \geq \theta - (2n\epsilon)/m$''; which is not true (since $\theta$ is the median of the distribution, and not the left-end point). Ok, this can be salvaged by saying that $\theta^{init}$ is estimate of the left-end point (i.e. $\theta - 1$). But then again, the confusion arises in the next line: ``The event $\theta^{init} \geq t_j* + (2n\epsilon)/m$ may occur only if for each of the $n/m$ observations in the set $I_{j^\star+1}...$''. Why ``only if''? It may well be that we observe both $0$ and $1$ for observations in $I_{j^\star+1}$ and observe only $0$'s in $I_{j^\star+2}$; this would also make the event ``$\theta^{init} \geq t_j^\star + (2n\epsilon)/m$'' happen.
\end{review}

\begin{response}
We thank Reviewer 1 for pointing on the problems with this example. As it turns out, the original example were missing the important ingredient of comparing our communication-limited estimator to the maximum of the samples within a bin. We have carefully went through this example and revised to add the missing part and resolve all other issues.  
\end{response}

\begin{review}
\begin{enumerate}
\item  Section III A, page 8: Extra braces in the indicator function in the definition of $B_i$ and the line after that.
\begin{response}
Fixed. 
\end{response}

\item Section III B, page 9, equation (7): Why is it $O(1/n)$? In the proof (Appendix VII A), $D*$ has $o(1/n)$; so after multiplication by $n$, we get $o(1)$. Could you clarify what $o(1/n)$ is hiding that makes it $O(1/n)$ in (7) instead of merely $o(1)$?

\begin{response}
Thank you for this comment. It made us realized that there was a mistake in the proof and we should have replaced the $o(1/n)$ term with $O(n^{-2})$. We now provide a more detailed derivation of the expansion of $D^\star$ as $n\to \infty$ that provides the second order term. 
\end{response}

### 2021-10-01 uniform-are-weirdos.tex
add detailed expansion in CEO proof

%
Denote by $D^\star$ the optimal MSE in the Gaussian CEO with $L$ observers and under a total sum-rate $r = r_1 + \ldots +r_L$. An expression for $D^\star$ as a function of $r$ is give as \cite[Eq. 10]{chen2004upper}:
\begin{equation} \label{eq:ceo_optimal_sumrate}
r = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
For the special case where $r = n$ and $L=n$, we have
\begin{equation} \label{eq:ceo_optimal_sumrate2}
n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
Consider the distributed encoding setting (iii) in the case where $f(x) = \Ncal(0,\sigma^2)$ and the prior on $\Theta$ is $\pi = \Ncal(0,\sigma_\theta^2)$. The Gaussian CEO problem of \cite{viswanathan1997quadratic} with a unit bitrate $r_1=\ldots = r_n =1$ at each terminal and blocklength $k=1$ reduces to our distributed setting (iii). Since $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describes the MSE in the CEO setting under an optimal allocation of the sum-rate $r = n$ among $n$ encoders, it provides a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. By considering the limit $n\rightarrow \infty$ in \eqref{eq:ceo_optimal_sumrate2}, we see that 
\[
D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + O(n^{-2}) =  \frac{4\sigma^2}{3n} + O(n^{-2}). 
\]
This implies Proposition~\ref{prop:CEO}. 
%We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the MSE in the CEO setting while enforcing the condition $r_1=\ldots = r_n = 1$. Indeed, an upper bound for the CEO MSE under the condition $r_1=\ldots = r_n = 1$ follows from \cite{KipnisRini2019}, and leads to
%\[
%D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
%\]
%which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.

>>>>

%
Denote by $D^\star$ the optimal MSE in the Gaussian CEO with $L$ observers and under a total sum-rate $r = r_1 + \ldots +r_L$. An expression for $D^\star$ as a function of $r$ is give as \cite[Eq. 10]{chen2004upper}:
\begin{equation} \label{eq:ceo_optimal_sumrate}
r = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
For the special case where $r = n$ and $L=n$, we have
\begin{equation} \label{eq:ceo_optimal_sumrate2}
n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
Consider the distributed encoding setting (iii) in the case where $f(x) = \Ncal(0,\sigma^2)$ and the prior on $\Theta$ is $\pi = \Ncal(0,\sigma_\theta^2)$. The Gaussian CEO problem of \cite{viswanathan1997quadratic} with a unit bitrate $r_1=\ldots = r_n =1$ at each terminal and blocklength $k=1$ reduces to our distributed setting (iii). Since $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describes the MSE in the CEO setting under an optimal allocation of the sum-rate $r = n$ among $n$ encoders, it provides a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. 
\newtext{By noting that $1/D^\star$ grows no faster than a polynomial in $n$ \cite{viswanathan1997quadratic}, we rely on the expansion
\begin{align*}
\left(\frac{\sigma_{\theta}^2}{D^\star}\right)^{1/n} 
= 1 + \frac{\log \left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{n}+\frac{\log^2\left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{2 n^2}+O\left(n^{-3}\right),
\end{align*}
to obtain that, in limit $n\rightarrow \infty$, \eqref{eq:ceo_optimal_sumrate2} behaves as 
\begin{align*}
D^\star = %\frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + O(n^{-2}) =  \frac{4\sigma^2}{3n} + O(n^{-2}). 
\frac{4 \sigma^2}{3 n}
+ \frac{16 \sigma^2}{9 n^2 \sigma_{\theta}^2 }-\frac{4 \sigma^2 \log \left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{9 n^2}
+O(n^{-3}).
\end{align*}
}
This implies Proposition~\ref{prop:CEO}. 
%We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the MSE in the CEO setting while enforcing the condition $r_1=\ldots = r_n = 1$. Indeed, an upper bound for the CEO MSE under the condition $r_1=\ldots = r_n = 1$ follows from \cite{KipnisRini2019}, and leads to
%\[
%D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
%\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
%\]
%which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.
